figures_manuscript

### 2024-10-21 pub_figures/manuscript-figures.Rmd
grouping

## Fig 4b: Groups
```{r groups, eval=FALSE}

@@

non-sig <- data.frame(x = c(-9, 0, 9), y = c(20, 0.5, 20))

@@

gg_all <- ggplot(DEGs_comb, aes(x=l2FC.blue, y=l2FC.red, label=symbol)) + # color=group, fill=group 
  geom_point(shape=21) +
  geom_hline(yintercept = c(-1,1), linewidth = 0.1) + 
  geom_vline(xintercept = c(-1,1), linewidth = 0.1) +
  coord_cartesian(xlim=c(-10,10),ylim = c(-10,10)) +
  geom_text_repel() +
  theme_bw() +
  removeGrid(x=T, y=T)
gg_all

gg_br <- ggplot(DEGs_comb[blue_red_genes,], aes(x=l2FC.blue, y=l2FC.red, label=symbol)) + # color=group, fill=group 
  geom_point(shape=21) +
  geom_text_repel() +
  coord_cartesian(xlim=c(-10,10),ylim = c(-10,10)) +
  theme_bw() +
  removeGrid(x=T, y=T)
gg_br

>>>>

## Fig 4b: Groups
```{r groups, eval=TRUE, out.width="50%", fig.show='hold'}

@@

non_sig <- data.frame(x = c(-9, 0, 9), y = c(20, 0.5, 20))

@@

gg_all <- ggplot(DEGs_comb, aes(x=l2FC.blue, y=l2FC.red, label=symbol)) + # color=group, fill=group 
  geom_point(shape=21) +
  geom_hline(yintercept = c(-1,1), linewidth = 0.1) + 
  geom_vline(xintercept = c(-1,1), linewidth = 0.1) +
  coord_cartesian(xlim=c(-10,10),ylim = c(-10,10)) +
  geom_text_repel(size=2, max.overlaps = 20) +
  theme_bw() +
  removeGrid(x=T, y=T)
gg_all

gg_br <- ggplot(DEGs_comb[blue_red_genes,], aes(x=l2FC.blue, y=l2FC.red, label=symbol)) + # color=group, fill=group 
  geom_point(shape=21) +
  geom_text_repel(size=3) +
  coord_cartesian(xlim=c(-10,10),ylim = c(-10,10)) +
  theme_bw() +
  removeGrid(x=T, y=T)
gg_br
